STA610 Case Study 1 Team 4 Report

### 2021-03-20 STA 610 Case Study 1 Report_Team 4.Rmd
Small formatting changes

* i stands for individuals and j stands for each state. 
* $\beta_{0,j}$ is the random intercept by state. 
* $\beta_{1}$ measures the fixed effect for date_num, the date variable.
* $\beta_{2}$ measures the fixed effect for mgstr, the dosage strength of reported drug in milligrams.
* $\beta_{3}$ measures the fixed effect for bulk_purchase is a binary variable that is represented by an indicator function I(bulk_purchase = Yes). 
* $\beta_{4}$ measures the fixed effect for the categorical variable Primary_Reason which contains three categories: Other or unknown, Self-treat and Enjoyment.
* $\beta_{5}$ measures the fixed effect for the categorical variable source

>>>>

* i stands for individuals and j stands for each state. 
* $\beta_{0,j}$: Random intercept by state
* $\beta_{1}$: Fixed effect for date_num, the date variable
* $\beta_{2}$: Fixed effect for mgstr, the dosage strength of reported drug in milligrams.
* $\beta_{3}$: Fixed effect for bulk_purchase is a binary variable that is represented by an indicator function I(bulk_purchase = Yes). 
* $\beta_{4}$: Fixed effect for the categorical variable Primary_Reason which contains three categories:     - Other or unknown
    - Self-treat
    - Enjoymen
* $\beta_{5}$ measures the fixed effect for the categorical variable source
